Active Learning for Level Set Estimation

### 2013-03-22 figurefactory/files/limno_bgape_pp_0_1.tex
Add batch/path planning; add summary; finish first draft

>>>>

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=1.6pt,
line width=0.2pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0) 
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_0_2.tex
Add batch/path planning; add summary; finish first draft

@@

>>>>

\addplot [
draw=red!50!white,
line width=0.6pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)(716.606060606061,-11.6363636363636)(627.030303030303,-18)(537.454545454546,-14.7272727272727)(447.878787878788,-7.63636363636364)(358.30303030303,-10.5454545454545)(0,-18)(0,-14.5454545454545)(0,-11.2727272727273)(0,-8)(0,-4)(0,0)(328.444444444444,-5.09090909090909)(388.161616161616,-2)(746.464646464646,0)(880.828282828283,-15.4545454545455)(925.616161616162,-8)(1045.05050505051,-18)(1104.76767676768,-11.0909090909091)(1104.76767676768,-5.45454545454546)(1119.69696969697,0)(1149.55555555556,-2.36363636363636)(1224.20202020202,-14.3636363636364)(1478,-18)(1478,-15.6363636363636)(1478,-12.9090909090909)(1478,-10.1818181818182)(1478,-7.63636363636364)(1478,-5.09090909090909)(1478,0) 
};

@@

\addplot [
color=lime,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (731.535353535354,-4.36363636363636)
};

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1478,0)
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_120_1.tex
Add batch/path planning; add summary; finish first draft

>>>>

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=1.6pt,
line width=0.2pt,
forget plot
]
coordinates{
 (149.292929292929,-8)(134.363636363636,-7.81818181818182)(119.434343434343,-8)(119.434343434343,-8.18181818181818)(134.363636363636,-8.36363636363636)(164.222222222222,-8.54545454545455)(238.868686868687,-7.81818181818182)(253.79797979798,-8.36363636363636)(403.090909090909,-8)(403.090909090909,-8.36363636363636)(447.878787878788,-8.72727272727273)(492.666666666667,-7.45454545454546)(507.59595959596,-7.45454545454546)(507.59595959596,-9.09090909090909)(552.383838383838,-7.45454545454546)(597.171717171717,-9.09090909090909)(612.10101010101,-7.81818181818182)(627.030303030303,-8.90909090909091)(641.959595959596,-8.54545454545455)(806.181818181818,-8.90909090909091)(821.111111111111,-8.18181818181818)(850.969696969697,-7.81818181818182)(955.474747474747,-10)(955.474747474747,-7.27272727272727)(1045.05050505051,-7.27272727272727)(1119.69696969697,-10.1818181818182)(1134.62626262626,-10.1818181818182)(1224.20202020202,-7.63636363636364)(1328.70707070707,-8)(1433.21212121212,-8.90909090909091)(1433.21212121212,-9.27272727272727) 
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_120_2.tex
Add batch/path planning; add summary; finish first draft

@@

>>>>

\addplot [
draw=red!50!white,
line width=0.6pt,
forget plot
]
coordinates{
 (149.292929292929,-8)(134.363636363636,-7.81818181818182)(119.434343434343,-8)(119.434343434343,-8.18181818181818)(134.363636363636,-8.36363636363636)(164.222222222222,-8.54545454545455)(238.868686868687,-7.81818181818182)(253.79797979798,-8.36363636363636)(403.090909090909,-8)(403.090909090909,-8.36363636363636)(447.878787878788,-8.72727272727273)(492.666666666667,-7.45454545454546)(507.59595959596,-7.45454545454546)(507.59595959596,-9.09090909090909)(552.383838383838,-7.45454545454546)(597.171717171717,-9.09090909090909)(612.10101010101,-7.81818181818182)(627.030303030303,-8.90909090909091)(641.959595959596,-8.54545454545455)(806.181818181818,-8.90909090909091)(821.111111111111,-8.18181818181818)(850.969696969697,-7.81818181818182)(955.474747474747,-10)(955.474747474747,-7.27272727272727)(1045.05050505051,-7.27272727272727)(1119.69696969697,-10.1818181818182)(1134.62626262626,-10.1818181818182)(1224.20202020202,-7.63636363636364)(1328.70707070707,-8)(1433.21212121212,-8.90909090909091)(1433.21212121212,-9.27272727272727) 
};

@@

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1433.21212121212,-9.27272727272727)
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_150_1.tex
Add batch/path planning; add summary; finish first draft

>>>>

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=1.6pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1433.21212121212,-9.27272727272727)(1418.28282828283,-8.72727272727273)(1388.42424242424,-9.81818181818182)(1298.84848484848,-10)(1194.34343434343,-7.63636363636364)(1104.76767676768,-7.45454545454546)(910.686868686869,-7.45454545454546)(895.757575757576,-9.81818181818182)(836.040404040404,-9.45454545454546)(806.181818181818,-9.09090909090909)(806.181818181818,-8.36363636363636)(627.030303030303,-8)(582.242424242424,-9.09090909090909)(552.383838383838,-7.27272727272727)(537.454545454546,-7.27272727272727)(507.59595959596,-7.27272727272727)(492.666666666667,-7.27272727272727)(492.666666666667,-9.09090909090909)(432.949494949495,-8.72727272727273)(432.949494949495,-7.63636363636364)(253.79797979798,-7.81818181818182)(223.939393939394,-8.54545454545455)(179.151515151515,-8.72727272727273)(164.222222222222,-7.63636363636364)(149.292929292929,-7.63636363636364)(134.363636363636,-7.63636363636364)(134.363636363636,-8.54545454545455)(119.434343434343,-8.54545454545455)(104.505050505051,-7.81818181818182)(89.5757575757576,-8)(89.5757575757576,-8.18181818181818) 
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_150_2.tex
Add batch/path planning; add summary; finish first draft

@@

>>>>

\addplot [
draw=red!50!white,
line width=0.6pt,
forget plot
]
coordinates{
 (1433.21212121212,-9.27272727272727)(1418.28282828283,-8.72727272727273)(1388.42424242424,-9.81818181818182)(1298.84848484848,-10)(1194.34343434343,-7.63636363636364)(1104.76767676768,-7.45454545454546)(910.686868686869,-7.45454545454546)(895.757575757576,-9.81818181818182)(836.040404040404,-9.45454545454546)(806.181818181818,-9.09090909090909)(806.181818181818,-8.36363636363636)(627.030303030303,-8)(582.242424242424,-9.09090909090909)(552.383838383838,-7.27272727272727)(537.454545454546,-7.27272727272727)(507.59595959596,-7.27272727272727)(492.666666666667,-7.27272727272727)(492.666666666667,-9.09090909090909)(432.949494949495,-8.72727272727273)(432.949494949495,-7.63636363636364)(253.79797979798,-7.81818181818182)(223.939393939394,-8.54545454545455)(179.151515151515,-8.72727272727273)(164.222222222222,-7.63636363636364)(149.292929292929,-7.63636363636364)(134.363636363636,-7.63636363636364)(134.363636363636,-8.54545454545455)(119.434343434343,-8.54545454545455)(104.505050505051,-7.81818181818182)(89.5757575757576,-8)(89.5757575757576,-8.18181818181818) 
};

@@

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (89.5757575757576,-8.18181818181818)
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_180_1.tex
Add batch/path planning; add summary; finish first draft

>>>>

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=1.6pt,
line width=0.2pt,
forget plot
]
coordinates{
 (89.5757575757576,-8.18181818181818)(104.505050505051,-8.36363636363636)(164.222222222222,-8.72727272727273)(179.151515151515,-7.63636363636364)(238.868686868687,-8.54545454545455)(268.727272727273,-8.18181818181818)(403.090909090909,-8.18181818181818)(418.020202020202,-7.81818181818182)(462.808080808081,-8.90909090909091)(477.737373737374,-7.27272727272727)(522.525252525253,-7.09090909090909)(567.313131313131,-7.27272727272727)(597.171717171717,-7.45454545454546)(612.10101010101,-8.90909090909091)(627.030303030303,-8.54545454545455)(627.030303030303,-8.36363636363636)(627.030303030303,-8.18181818181818)(791.252525252525,-8.72727272727273)(791.252525252525,-9.09090909090909)(821.111111111111,-9.45454545454546)(836.040404040404,-8)(850.969696969697,-9.63636363636364)(880.828282828283,-7.63636363636364)(1000.26262626263,-7.27272727272727)(1059.9797979798,-10.1818181818182)(1119.69696969697,-7.45454545454546)(1268.9898989899,-7.81818181818182)(1343.63636363636,-10)(1373.49494949495,-8.18181818181818)(1418.28282828283,-9.63636363636364)(1433.21212121212,-9.45454545454546) 
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_180_2.tex
Add batch/path planning; add summary; finish first draft

@@

>>>>

\addplot [
draw=red!50!white,
line width=0.6pt,
forget plot
]
coordinates{
 (89.5757575757576,-8.18181818181818)(104.505050505051,-8.36363636363636)(164.222222222222,-8.72727272727273)(179.151515151515,-7.63636363636364)(238.868686868687,-8.54545454545455)(268.727272727273,-8.18181818181818)(403.090909090909,-8.18181818181818)(418.020202020202,-7.81818181818182)(462.808080808081,-8.90909090909091)(477.737373737374,-7.27272727272727)(522.525252525253,-7.09090909090909)(567.313131313131,-7.27272727272727)(597.171717171717,-7.45454545454546)(612.10101010101,-8.90909090909091)(627.030303030303,-8.54545454545455)(627.030303030303,-8.36363636363636)(627.030303030303,-8.18181818181818)(791.252525252525,-8.72727272727273)(791.252525252525,-9.09090909090909)(821.111111111111,-9.45454545454546)(836.040404040404,-8)(850.969696969697,-9.63636363636364)(880.828282828283,-7.63636363636364)(1000.26262626263,-7.27272727272727)(1059.9797979798,-10.1818181818182)(1119.69696969697,-7.45454545454546)(1268.9898989899,-7.81818181818182)(1343.63636363636,-10)(1373.49494949495,-8.18181818181818)(1418.28282828283,-9.63636363636364)(1433.21212121212,-9.45454545454546) 
};

@@

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1433.21212121212,-9.45454545454546)
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_30_1.tex
Add batch/path planning; add summary; finish first draft

>>>>

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=1.6pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546) 
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_30_2.tex
Add batch/path planning; add summary; finish first draft

@@

>>>>

\addplot [
draw=red!50!white,
line width=0.6pt,
forget plot
]
coordinates{
 (1478,0)(1268.9898989899,-8.18181818181818)(1254.06060606061,-9.27272727272727)(1164.48484848485,-8.54545454545455)(1149.55555555556,-8.18181818181818)(1134.62626262626,-7.81818181818182)(1119.69696969697,-8.90909090909091)(1104.76767676768,-7.63636363636364)(1074.90909090909,-7.45454545454546)(1074.90909090909,-9.09090909090909)(1059.9797979798,-9.09090909090909)(1030.12121212121,-7.27272727272727)(1015.19191919192,-7.27272727272727)(970.40404040404,-9.27272727272727)(910.686868686869,-7.09090909090909)(880.828282828283,-9.09090909090909)(865.89898989899,-9.09090909090909)(865.89898989899,-7.09090909090909)(791.252525252525,-8.90909090909091)(791.252525252525,-7.27272727272727)(761.393939393939,-7.27272727272727)(746.464646464646,-8.72727272727273)(716.606060606061,-8.54545454545455)(686.747474747475,-7.63636363636364)(671.818181818182,-8.18181818181818)(656.888888888889,-8)(597.171717171717,-7.09090909090909)(537.454545454546,-8.72727272727273)(223.939393939394,-8.36363636363636)(194.080808080808,-7.09090909090909)(0,-9.45454545454546) 
};

@@

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (0,-9.45454545454546)
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_60_1.tex
Add batch/path planning; add summary; finish first draft

>>>>

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=1.6pt,
line width=0.2pt,
forget plot
]
coordinates{
 (0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727)(1418.28282828283,-8.90909090909091) 
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_60_2.tex
Add batch/path planning; add summary; finish first draft

@@

>>>>

\addplot [
draw=red!50!white,
line width=0.6pt,
forget plot
]
coordinates{
 (0,-9.45454545454546)(209.010101010101,-8.18181818181818)(268.727272727273,-8.72727272727273)(298.585858585859,-7.81818181818182)(313.515151515152,-7.81818181818182)(313.515151515152,-8.90909090909091)(373.232323232323,-9.09090909090909)(388.161616161616,-9.09090909090909)(418.020202020202,-7.63636363636364)(492.666666666667,-9.27272727272727)(522.525252525253,-9.27272727272727)(522.525252525253,-7.81818181818182)(567.313131313131,-8)(567.313131313131,-9.09090909090909)(836.040404040404,-8.36363636363636)(836.040404040404,-9.63636363636364)(850.969696969697,-9.81818181818182)(865.89898989899,-8)(940.545454545455,-10.1818181818182)(955.474747474747,-10.1818181818182)(1074.90909090909,-10.3636363636364)(1209.27272727273,-7.63636363636364)(1224.20202020202,-10.1818181818182)(1239.13131313131,-10.1818181818182)(1283.91919191919,-7.81818181818182)(1313.77777777778,-10)(1358.56565656566,-9.81818181818182)(1358.56565656566,-8.18181818181818)(1403.35353535354,-8.72727272727273)(1403.35353535354,-9.27272727272727)(1418.28282828283,-8.90909090909091) 
};

@@

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1418.28282828283,-8.90909090909091)
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_90_1.tex
Add batch/path planning; add summary; finish first draft

>>>>

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=1.6pt,
line width=0.2pt,
forget plot
]
coordinates{
 (1418.28282828283,-8.90909090909091)(1433.21212121212,-9.09090909090909)(1418.28282828283,-9.45454545454546)(1403.35353535354,-8.54545454545455)(1388.42424242424,-8.36363636363636)(1373.49494949495,-9.81818181818182)(1328.70707070707,-10)(1298.84848484848,-7.81818181818182)(1239.13131313131,-7.63636363636364)(1149.55555555556,-7.45454545454546)(1134.62626262626,-7.45454545454546)(1104.76767676768,-10.1818181818182)(1089.83838383838,-10.1818181818182)(1074.90909090909,-10.1818181818182)(925.616161616162,-7.45454545454546)(925.616161616162,-10)(880.828282828283,-9.81818181818182)(865.89898989899,-7.81818181818182)(821.111111111111,-9.27272727272727)(612.10101010101,-8.72727272727273)(597.171717171717,-8.90909090909091)(567.313131313131,-7.63636363636364)(477.737373737374,-7.63636363636364)(418.020202020202,-8.54545454545455)(388.161616161616,-8.36363636363636)(388.161616161616,-8.18181818181818)(268.727272727273,-8)(194.080808080808,-7.81818181818182)(164.222222222222,-8)(164.222222222222,-8.18181818181818)(149.292929292929,-8) 
};

### 2013-03-22 figurefactory/files/limno_bgape_pp_90_2.tex
Add batch/path planning; add summary; finish first draft

@@

>>>>

\addplot [
draw=red!50!white,
line width=0.6pt,
forget plot
]
coordinates{
 (1418.28282828283,-8.90909090909091)(1433.21212121212,-9.09090909090909)(1418.28282828283,-9.45454545454546)(1403.35353535354,-8.54545454545455)(1388.42424242424,-8.36363636363636)(1373.49494949495,-9.81818181818182)(1328.70707070707,-10)(1298.84848484848,-7.81818181818182)(1239.13131313131,-7.63636363636364)(1149.55555555556,-7.45454545454546)(1134.62626262626,-7.45454545454546)(1104.76767676768,-10.1818181818182)(1089.83838383838,-10.1818181818182)(1074.90909090909,-10.1818181818182)(925.616161616162,-7.45454545454546)(925.616161616162,-10)(880.828282828283,-9.81818181818182)(865.89898989899,-7.81818181818182)(821.111111111111,-9.27272727272727)(612.10101010101,-8.72727272727273)(597.171717171717,-8.90909090909091)(567.313131313131,-7.63636363636364)(477.737373737374,-7.63636363636364)(418.020202020202,-8.54545454545455)(388.161616161616,-8.36363636363636)(388.161616161616,-8.18181818181818)(268.727272727273,-8)(194.080808080808,-7.81818181818182)(164.222222222222,-8)(164.222222222222,-8.18181818181818)(149.292929292929,-8) 
};

@@

\addplot [
color=red,
draw=black,
only marks,
mark=*,
mark options={solid},
mark size=3pt,
line width=0.2pt,
forget plot
]
coordinates{
 (149.292929292929,-8)
};

### 2013-03-22 msthpres.tex
Add batch/path planning; add summary; finish first draft

\documentclass[10pt,mathserif,serif]{beamer}
%\documentclass[10pt,mathserif,serif,draft,handout]{beamer}

@@

@@

\begin{frame}
\begin{enumerate}
\item bla
\end{enumerate}
\end{frame}

>>>>

%\documentclass[10pt,mathserif,serif]{beamer}
\documentclass[10pt,mathserif,serif,handout]{beamer}

@@

\begin{frame}
\begin{itemize}
\item<1-> Up to this point we have assumed a fixed cost per sample
\item<2-> What about the traveling distance between measurements?
\item<3-> Plan ahead:
\begin{itemize}
\item Select a \emph{batch} of sampling locations
\item Connect them using a Euclidean TSP path
\item Traverse the path and collect measurements
\end{itemize}
\end{itemize}

\begin{center}
\color{white}
\includegraphics<1-3>[draft,width=3.78in]{figures/limno_bgape_pp_0_0}
\color{black}
\includegraphics<4>[width=3.78in]{figures/limno_bgape_pp_0_0}
\includegraphics<5>[width=3.78in]{figures/limno_bgape_pp_0_1}
\includegraphics<6>[width=3.78in]{figures/limno_bgape_pp_0_2}
\includegraphics<7>[width=3.78in]{figures/limno_bgape_pp_30_0}
\includegraphics<8>[width=3.78in]{figures/limno_bgape_pp_30_1}
\includegraphics<9>[width=3.78in]{figures/limno_bgape_pp_30_2}
\includegraphics<10>[width=3.78in]{figures/limno_bgape_pp_60_0}
\includegraphics<11>[width=3.78in]{figures/limno_bgape_pp_60_1}
\includegraphics<12>[width=3.78in]{figures/limno_bgape_pp_60_2}
\includegraphics<13>[width=3.78in]{figures/limno_bgape_pp_90_0}
\includegraphics<14>[width=3.78in]{figures/limno_bgape_pp_90_1}
\includegraphics<15>[width=3.78in]{figures/limno_bgape_pp_90_2}
\includegraphics<16>[width=3.78in]{figures/limno_bgape_pp_120_0}
\includegraphics<17>[width=3.78in]{figures/limno_bgape_pp_120_1}
\includegraphics<18>[width=3.78in]{figures/limno_bgape_pp_120_2}
\includegraphics<19>[width=3.78in]{figures/limno_bgape_pp_150_0}
\includegraphics<20>[width=3.78in]{figures/limno_bgape_pp_150_1}
\includegraphics<21>[width=3.78in]{figures/limno_bgape_pp_150_2}
\includegraphics<22>[width=3.78in]{figures/limno_bgape_pp_180_0}
\includegraphics<23>[width=3.78in]{figures/limno_bgape_pp_180_1}
\includegraphics<24>[width=3.78in]{figures/limno_bgape_pp_180_2}
\includegraphics<25>[width=3.78in]{figures/limno_bgape_pp_210_0}
\includegraphics<26>[width=2.7in]{figures/ev_bgape_pp}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Summary
\end{center}
\vspace{-1em}
\begin{itemize}
\item<1-> \acl algorithm:
\begin{itemize}
\item<2-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
\item<3-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
\end{itemize}
\item<4-> Two useful extensions:
\begin{itemize}
\item<5-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
\item<6-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
\end{itemize}
\item<7-> Look out for algae when swimming in Lake Zurich! =)
\end{itemize}
\end{frame}

\begin{frame}
\begin{center}
\large Questions?\\
\vspace{2em}
\includegraphics[width=3in]{figures/dilbert}
\end{center}
\end{frame}
